
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Classification Churn

+ `State:` the US state in which the customer resides, indicated by a two-letter abbreviation; for example, OH or NJ
+ `Account Length:` the number of days that this account has been active
+ `Area Code:` the three-digit area code of the corresponding customer’s phone number
+ `Int’l Plan:` whether the customer has an international calling plan: yes/no
+ `VMail Plan:` whether the customer has a voice mail feature: yes/no
+ `VMail Message:` presumably the average number of voice mail messages per month
+ `Day Mins:` the total number of calling minutes used during the day
+ `Day Calls:` the total number of calls placed during the day
+ `Day Charge:` the billed cost of daytime calls
+ `Eve Mins, Eve Calls, Eve Charge:` the billed cost for calls placed during the evening
+ `Night Mins, Night Calls, Night Charge:` the billed cost for calls placed during nighttime
+ `Intl Mins, Intl Calls, Intl Charge:` the billed cost for international calls
+ `CustServ Calls:` the number of calls placed to Customer Service
+ `Churn?:` whether the customer left the service: true/false


```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(gridExtra)
library(dplyr)
library(corrplot)
library(pROC)
library(caTools)
library(plotROC)
library(caret)
library(ggplot2)
library(corrplot)
if (!require("rpart")) install.packages("rpart")
library("rpart")
if (!require("rpart.plot")) install.packages("rpart.plot")
library("rpart.plot")
library(caTools)
library(ROCR)
library(gridExtra)
if (!require("ROSE")) install.packages("ROSE")
library("ROSE")

set.seed(123)
churn_train <-read.csv("C:/Users/409-21/Desktop/MA/churn_train.csv")
str(churn_train)

churn_validation <-read.csv("C:/Users/409-21/Desktop/MA/churn_validation.csv")
str(churn_validation)
```

```{r}
prop.table(table(Target_Ratio=churn_train$Churn))
```

```{r}
table(churn_train$State)
# plot a histogram for this variable
with(churn_train, hist(Account.length ))
table(churn_train$Area.code)
table(churn_train$International.plan)
table(churn_train$Voice.mail.plan)
# plot a histogram for this variable
with(churn_train, hist(Number.vmail.messages))
# plot a histogram for this variable
with(churn_train, hist(Customer.service.calls))

```

```{r}

# histogram of age by income group
ggplot(churn_train) + aes(x=as.numeric(Total.day.calls), group=Churn, fill=Churn) + 
  geom_histogram(binwidth=1, color='black')
```

```{r}

# histogram of age by income group
ggplot(churn_train) + aes(x=as.numeric( Total.night.calls), group=Churn, fill=Churn) + 
  geom_histogram(binwidth=1, color='black')
```
```{r}
# Churn By State

# histogram of age by income group
ggplot(churn_train) + aes(x=as.numeric(State), group=Churn, fill=Churn) + 
  geom_histogram(binwidth=1, color='black')
```

```{r}
# Churn By Area Code

# histogram of age by income group
ggplot(churn_train) + aes(x=as.numeric(Area.code), group=Churn, fill=Churn) + 
  geom_histogram(binwidth=1, color='black')
```

```{r}
# Churn By Customers with International plan

# histogram of age by income group
ggplot(churn_train) + aes(x=as.numeric(International.plan ), group=Churn, fill=Churn) + 
  geom_histogram(binwidth=1, color='black')
```

```{r}
# Churn By Customers with Voice mail plan

# histogram of age by income group
ggplot(churn_train) + aes(x=as.numeric(Voice.mail.plan), group=Churn, fill=Churn) + 
  geom_histogram(binwidth=1, color='black')
```


```{r}
summary(churn_train$Customer.service.calls)
summary(churn_train$State)
 
```

```{r}

daymin <- ggplot(churn_train, aes(Churn, Total.day.minutes, fill = Churn)) + geom_boxplot(alpha = 0.8) + theme(legend.position = "null")
evemin <- ggplot(churn_train, aes(Churn, Total.eve.minutes, fill = Churn)) + geom_boxplot(alpha = 0.8) + theme(legend.position = "null")
nitmin <- ggplot(churn_train, aes(Churn, Total.night.minutes, fill = Churn)) + geom_boxplot(alpha = 0.8) + theme(legend.position = "null")
intmin <- ggplot(churn_train, aes(Churn, Total.intl.minutes, fill = Churn)) + geom_boxplot(alpha = 0.8) + theme(legend.position = "null")
daycal <- ggplot(churn_train, aes(Churn, Total.day.calls, fill = Churn)) + geom_boxplot(alpha = 0.8) + theme(legend.position = "null")
evecal <- ggplot(churn_train, aes(Churn, Total.eve.calls, fill = Churn)) + geom_boxplot(alpha = 0.8) + theme(legend.position = "null")
nitcal <- ggplot(churn_train, aes(Churn, Total.night.calls, fill = Churn)) + geom_boxplot(alpha = 0.8) + theme(legend.position = "null")
intcal <- ggplot(churn_train, aes(Churn, Total.intl.calls, fill = Churn)) + geom_boxplot(alpha = 0.8) + theme(legend.position = "null")
grid.arrange(daymin, evemin, nitmin, intmin, 
             daycal, evecal, nitcal, intcal, 
             ncol = 4, nrow = 2)
```


```{r}

# Create correlation plot for numerical features
corrplot(cor(churn_train[sapply(churn_train, is.numeric)]))
```

```{r}
churn_train$total_day_charge <- NULL
churn_train$total_eve_charge <- NULL
churn_train$total_night_charge <- NULL
churn_train$total_intl_charge <- NULL
churn_validation$total_day_charge <- NULL
churn_validation$total_eve_charge <- NULL
churn_validation$total_night_charge <- NULL
churn_validation$total_intl_charge <- NULL
```


```{r}

#Split dataset train and test. 70% train, 30% test data
split <- sample.split(churn_train$Churn, SplitRatio = 0.7)
train <- subset(churn_train, split == TRUE)
test <- subset(churn_train, split == FALSE)

prop.table(table(Target_Ratio=train$Churn))
prop.table(table(Target_Ratio=test$Churn))

#Tranforming variables to numeric form 
#no=1, yes =0
#str(train)
train$Churn <- as.integer(train$Churn)
train$Churn[train$Churn == "1"] <- 1
train$Churn[train$Churn == "2"] <- 0

train$International.plan <-as.integer(train$International.plan)
train$International.plan[train$International.plan == "1"] <- 0
train$International.plan[train$International.plan == "2"] <- 1

train$Voice.mail.plan <- as.integer(train$Voice.mail.plan)
train$Voice.mail.plan[train$Voice.mail.plan == "1"] <- 0
train$Voice.mail.plan[train$Voice.mail.plan == "2"] <- 1

test$Churn <- as.integer(test$Churn)
test$Churn[test$Churn == "1"] <- 1
test$Churn[test$Churn == "2"] <- 0

test$International.plan <-as.integer(test$International.plan)
test$International.plan[test$International.plan == "1"] <- 0
test$International.plan[test$International.plan == "2"] <- 1

test$Voice.mail.plan <- as.integer(test$Voice.mail.plan)
test$Voice.mail.plan[test$Voice.mail.plan == "1"] <- 0
test$Voice.mail.plan[test$Voice.mail.plan == "2"] <- 1

#Copy data for tree model
train_tree <- train
test_tree <- test


```


```{r}
#Validation data transformation
churn_validation$Churn <- as.integer(churn_validation$Churn)
churn_validation$Churn[churn_validation$Churn == "1"] <- 0
churn_validation$Churn[churn_validation$Churn == "2"] <- 1

churn_validation$International.plan <-as.integer(churn_validation$International.plan)
churn_validation$International.plan[churn_validation$International.plan == "1"] <- 0
churn_validation$International.plan[churn_validation$International.plan == "2"] <- 1

churn_validation$Voice.mail.plan <- as.integer(churn_validation$Voice.mail.plan)
churn_validation$Voice.mail.plan[churn_validation$Voice.mail.plan == "1"] <- 0
churn_validation$Voice.mail.plan[churn_validation$Voice.mail.plan == "2"] <- 1

prop.table(table(Target_Ratio=churn_validation$Churn))
prop.table(table(Target_Ratio=churn_train$Churn))


```

# Create Model

## Model 1 Logistic Regression

```{r}
# ----------------------------------
# specify predictive model
# ----------------------------------
model <- {Churn ~ Account.length + Area.code + International.plan + Voice.mail.plan + Number.vmail.messages +
    Total.day.minutes + Total.day.calls + Total.eve.minutes + Total.eve.calls + 
    Total.night.minutes + Total.night.calls+ Total.intl.minutes + Total.intl.calls + Customer.service.calls}

# ----------------------------------
# fit logistic regression model 
# ----------------------------------
churn_fit <- glm(model, family=binomial, data=train)
print(summary(churn_fit))
#print(anova(churn_fit, test="Chisq"))

# compute predicted probability of churn
test$Predict_Prob_Churn <- predict.glm(churn_fit, test, type = "response") 
```

```{r}
# Importance of features
varImp(churn_fit)
```


```{r}

test$Predict_Response <- ifelse((test$Predict_Prob_Churn > 0.5), 'TRUE', 'FALSE')

confusion_matrix <- table(test$Predict_Response, test$Churn)
cat("\nConfusion Matrix (rows=Predicted Response, columns=Actual Choice\n")
print(confusion_matrix)
predictive_accuracy <- (confusion_matrix[1,1] + confusion_matrix[2,2])/sum(confusion_matrix)
predictive_precision <- confusion_matrix[1,1]/(confusion_matrix[1,1]+ confusion_matrix[2,1])
predictive_recall <- confusion_matrix[1,1]/(confusion_matrix[1,1]+ confusion_matrix[2,2])
cat("\nPercent Accuracy: ", round(predictive_accuracy * 100, digits = 2))
cat("\nPercent Precision: ", round(predictive_precision * 100, digits = 2))
cat("\nPercent Recall: ", round(predictive_recall * 100, digits = 2))
```
```{r}

roc_logistic = roc.curve(response = test$Churn, predicted = test$Predict_Prob_Churn, col = "#45a163")

```


## Model 2 Decision Tree 

```{r, warning=FALSE, message=FALSE}

model <- {Churn ~ Account.length + Area.code + International.plan + Voice.mail.plan + Number.vmail.messages +
    Total.day.minutes + Total.day.calls + Total.eve.minutes + Total.eve.calls + 
    Total.night.minutes + Total.night.calls+ Total.intl.minutes + Total.intl.calls + Customer.service.calls}


tree = rpart(model, data = train_tree, method="class")
rpart.plot(tree)
pred_tree = predict(tree, test_tree, type = 'class')
pred_tree_prob = predict(tree, test_tree, type='prob')[,2]

confusion_matrix = table(actual=test_tree$Churn, predicted=pred_tree)
cat("\nConfusion Matrix (rows=Predicted Response, columns=Actual Choice\n")
print(confusion_matrix)

predictive_accuracy <- (confusion_matrix[1,1] + confusion_matrix[2,2])/sum(confusion_matrix)
predictive_precision <- confusion_matrix[1,1]/(confusion_matrix[1,1]+ confusion_matrix[2,1])
predictive_recall <- confusion_matrix[1,1]/(confusion_matrix[1,1]+ confusion_matrix[2,2])
cat("\nPercent Accuracy: ", round(predictive_accuracy * 100, digits = 2))
cat("\nPercent Precision: ", round(predictive_precision * 100, digits = 2))
cat("\nPercent REcall: ", round(predictive_recall * 100, digits = 2))

roc_tree = roc.curve(response = test_tree$Churn, pred_tree_prob, col = "#0d84da")


```

## Scoring on Validation Data (Decision Tree)

```{r, warning=FALSE, message=FALSE}


pred_tree = predict(tree, churn_validation, type = 'class')
pred_tree_prob = predict(tree, churn_validation, type='prob')[,2]

confusion_matrix = table(actual=churn_validation$Churn, predicted=pred_tree)
cat("\nConfusion Matrix (rows=Predicted Response, columns=Actual Choice\n")
print(confusion_matrix)

predictive_accuracy <- (confusion_matrix[1,1] + confusion_matrix[2,2])/sum(confusion_matrix)
predictive_precision <- confusion_matrix[1,1]/(confusion_matrix[1,1]+ confusion_matrix[2,1])
predictive_recall <- confusion_matrix[1,1]/(confusion_matrix[1,1]+ confusion_matrix[2,2])
cat("\nPercent Accuracy: ", round(predictive_accuracy * 100, digits = 2))
cat("\nPercent Precision: ", round(predictive_precision * 100, digits = 2))
cat("\nPercent REcall: ", round(predictive_recall * 100, digits = 2))

roc_tree = roc.curve(response = churn_validation$Churn, pred_tree_prob, col = "#0d84da")


```
## Scoring on Validation Data (Logistic Regression)

```{r, warning=FALSE, message=FALSE}


churn_validation$Predict_Prob_Churn <- predict.glm(churn_fit, churn_validation, type = "response") 

churn_validation$Predict_Response <- ifelse((churn_validation$Predict_Prob_Churn > 0.5), 'TRUE', 'FALSE')

confusion_matrix <- table(churn_validation$Predict_Response, churn_validation$Churn)
cat("\nConfusion Matrix (rows=Predicted Response, columns=Actual Choice\n")
print(confusion_matrix)
predictive_accuracy <- (confusion_matrix[1,1] + confusion_matrix[2,2])/sum(confusion_matrix)
predictive_precision <- confusion_matrix[1,1]/(confusion_matrix[1,1]+ confusion_matrix[2,1])
predictive_recall <- confusion_matrix[1,1]/(confusion_matrix[1,1]+ confusion_matrix[2,2])
cat("\nPercent Accuracy: ", round(predictive_accuracy * 100, digits = 2))
cat("\nPercent Precision: ", round(predictive_precision * 100, digits = 2))
cat("\nPercent REcall: ", round(predictive_recall * 100, digits = 2))

roc_logistic = roc.curve(response = churn_validation$Churn, predicted = churn_validation$Predict_Prob_Churn, col = "#45a163")

```

## Cross Validation for Logistic Regression
```{r, warning=FALSE, message=FALSE}

#10 fold cv
ctrl <- trainControl(method = "cv", number = 10, savePredictions = TRUE)

mod_fit <- train(model, data=train, method="glm", family="binomial", trControl = ctrl, tuneLength = 5)

# Predict our cross validation data
pred = predict(mod_fit, newdata=churn_validation)

#Convert to numeric value
pred_response <- ifelse((pred > 0.5), 1, 0)

confusion_matrix <- table(pred_response, churn_validation$Churn)
cat("\nConfusion Matrix (rows=Predicted Response, columns=Actual Choice\n")
print(confusion_matrix)
predictive_accuracy <- (confusion_matrix[1,1] + confusion_matrix[2,2])/sum(confusion_matrix)
predictive_precision <- confusion_matrix[1,1]/(confusion_matrix[1,1]+ confusion_matrix[2,1])
predictive_recall <- confusion_matrix[1,1]/(confusion_matrix[1,1]+ confusion_matrix[2,2])
cat("\nPercent Accuracy: ", round(predictive_accuracy * 100, digits = 2))
cat("\nPercent Precision: ", round(predictive_precision * 100, digits = 2))
cat("\nPercent REcall: ", round(predictive_recall * 100, digits = 2))

roc1 = roc.curve(response = churn_validation$Churn, predicted = pred, col = "#45a163")

```


## Lift Calculation for validation dataset

```{r, warning=FALSE, message=FALSE}

baseline_response_rate <- as.numeric(table(churn_validation$Churn)[2])/nrow(churn_validation)
    
lift <- function(x, baseline_response_rate) {
    mean(x) / baseline_response_rate
    }
    
#creating 10 decile 
churn_validation$decile <- ntile(churn_validation$Predict_Prob_Churn, 10)

```

```{r}

# define response as 0/1 binary 
churn_validation$response_binary <- as.numeric(churn_validation$Churn)

cat("\nLift Chart Values by Decile:\n")    
print(by(churn_validation$response_binary, churn_validation$decile, 
    function(x) lift(x, baseline_response_rate)))    

```

```{r, warning=FALSE, message=FALSE}
# 
churn_validation_decile <- churn_validation %>% filter(decile >= 7 )

confusion_matrix <- table(churn_validation_decile$Predict_Response, churn_validation_decile$Churn)
cat("\nConfusion Matrix (rows=Predicted Response, columns=Actual Choice\n")
print(confusion_matrix)
predictive_accuracy <- (confusion_matrix[1,1] + confusion_matrix[2,2])/sum(confusion_matrix)                                              
cat("\nPercent Accuracy: ", round(predictive_accuracy * 100, digits = 1))

```


## Cost Calculation

```{r, warning=FALSE, message=FALSE}

benefit <- function(confMatrix) {
  tp <- confMatrix[2,2]; fn <- confMatrix[1,1]
  fp <- confMatrix[1,2]; tn <- confMatrix[2,1]
  
  tp.cost <- 80      ; fn.cost <- 300
  fp.cost <- 80      ; tn.cost <- 0
  
  return(tp*tp.cost + fn*fn.cost + fp*fp.cost + tn*tn.cost )
}

benefit(table(churn_validation_decile$Predict_Response, churn_validation_decile$Churn))

```
